\documentclass[twoside,openright]{scrreprt}
\usepackage[a4paper, inner=4.2cm, outer=2.1cm, top=2.7cm, bottom=5.8cm]{geometry}  % Set the margins

\usepackage[msc]{tugrazthesis}
\usepackage{filecontents}  % for the integrated bibliography file (backwards compatibility)



% \usepackage{fancyhdr}  % Load the package
% \pagestyle{fancy}      % Use the 'fancy' page style
% \renewcommand{\headrulewidth}{0pt}
% \fancyhf{}             % Clear existing header and footer
% \fancyfoot[C]{\thepage} % Place page number in the center of the footer
% \fancypagestyle{plain}{
%   \fancyhf{}             % Clear header and footer for plain style
%   \renewcommand{\headrulewidth}{0pt} % Remove the top line
%   \fancyfoot[C]{\thepage} % Center the page number in the footer for chapter pages
% }





\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage[american]{babel}
\usepackage[babel=true]{csquotes}
\usepackage[
    backend=bibtex,
    maxnames=99,
    style=numeric,
]{biblatex}
\addbibresource{helper/references.bib}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,calligraphy}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{tikzmark,calc}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{cleveref}


% for references "Figure x.x" instead of "x.x"
\crefname{figure}{Figure}{Figures}
\crefname{section}{Section}{Sections}
\crefname{algorithm}{Algorithm}{Algorithms}
\crefname{table}{Table}{Tables}
\crefname{chapter}{Chapter}{Chapters}
\crefname{definition}{Definition}{Definitions}
% Redefine cleveref format for subfigures to include parentheses only around the subfigure label
\usepackage{pgfplots}
\usepackage{graphicx} % For including graphics

\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

\usepackage{changepage}  % Required for adjusting margins



\newcommand{\prog}{ClustArg\ignorespaces}

\definecolor{c1}{HTML}{1E3E62}
\definecolor{c2}{HTML}{FF6500}
\definecolor{c3}{HTML}{629584}

\newcommand{\cA}{c1}
\newcommand{\cB}{c2}
\newcommand{\cC}{c3}

\begin{document}
\include{helper/macros}



%--- INFORMATION FOR TITLEPAGE -------------------------------------------------

% Your name including previous academic degrees (optional argument sets a different \author{}):
\thesisauthor[Firstname Lastname]{Christian Pasero, BSc}

% Title of your thesis (optional argument sets a different \title{}):
\thesistitle[Short Thesis Title]{Computation of Clustered\\Argumentation Frameworks via\\Boolean Satisfiability}

% Date of completion (optional argument sets a different \date{})
\thesisdate[ ]{\today}

% Supervisor headline (select male/female/plural version)
\supervisortitle{\germanenglish{Betreuer}{Supervisor}}

% Supervisor info
\supervisor{
Johannes P. Wallner, Assoc.Prof. Dipl.-Ing. Dr.techn. BSc.\\
Institute of Software Technology
}


%\academicdegree{Diplom-Ingenieur/Diplom-Ingenieurin}
\academicdegree{Master of Science}

% Name of your degree programme according to your curriculum (only for msc/diplom
\curriculum{Computer Science}
%--- FRONT MATTER --------------------------------------------------------------

% Insert title page and affidavit

\printthesistitle

% \include{docs/dev_notes}

% Other front matter you may want to include

\chapter*{Abstract}
Argumentation frameworks (AFs) are a fundamental approach to formalize argumentative reasoning within artificial intelligence (AI). However, as the complexity of the argumentation frameworks increases, analyzing their structures and concluding something from them becomes challenging. Clustering is a method to decrease complexity by grouping multiple arguments into so-called clusters and simplifying the argumentation framework without drawing erroneous conclusions.

Since clustering argumentation frameworks is a relatively new concept, algorithmic approaches were not studied thoroughly yet. This thesis investigates the application of Boolean Satisfiability in creating and transforming clustered argumentation frameworks. We develop algorithms for determining if a given clustering is faithful, i.e., does not lead to erroneous conclusions, and to compute faithful clusterings by concretizations (extraction from clusters) until faithfulness is reached. We consider the stable argumentation semantics and the concepts of conflict-free sets and admissible sets. Moreover, we study variants based on Breadth-First-Search (BFS) and Depth-First-Search (DFS) and refinements of our algorithms.

We provide an empirical evaluation of an implementation of our algorithms. The results indicate that depending on the structure and size of the argumentation framework, one procedure performs better than the other. While the refinements do not show improvement for admissible and stable semantics, for conflict-free sets our refinement improves performance. For the two procedures of determining faithfulness or spuriousness, BFS and DFS, both find applicability in terms of runtime performance for all of the examined semantics. While BFS is more efficient on small argumentation frameworks (with a size of up to 10 arguments), DFS outperforms BFS on more complex argumentation frameworks.





\chapter*{Kurzfassung}

Argumentationssysteme sind ein grundlegender Bestandteil zur Formalisierung von argumentativen Szenarien im Forschungsgebiet der Künstlichen Intelligenz. Eine große Problemstellung stellt dabei die Skalierung der Systeme dar. Durch die Zunahme der Komplexität ist das Analysieren von Strukturen und Mustern in einem Argumentationssystem eine Herausforderung. Diese Herausforderung kann durch Clustering vereinfacht werden. Clustering ist eine Verfahren bei dem Argumente in sogenannten ''Clustern`` gruppiert werden, sodass keine falschen Schlussfolgerungen daraus geschlossen werden können.

Da das Clustering von Argumentationssystemen ein relativ neues Konzept ist, wurde dahingehend noch nicht ausreichend geforscht. Diese Arbeit beschäftigt sich mit der Anwendung der Erfüllbarkeit von boolschen Formeln im Zusammenhang mit der Transformation von geclusterten Argumentationssystemen. Dabei wurden Algorithmen zur Feststellung von \emph{faithfulness} (ein geclustertes Argumentationssystem ist faithful, wenn keine falschen Schlussfolgerungen daraus geschlossen werden können) entwickelt. Zusätzlich wurde ein weiterer Algorithmus entwickelt, der ein nicht-faithful Argumentationssystem so transformiert, dass es faithful wird. Dabei haben wir drei Semantiken berücksichtigt: conflict-free, admissible und stable. Zusätzlich haben wir verschiedene Algorithmen, wie die Breitensuche und die Tiefensuche und noch weitere Verfeinerungen/Optimierungen je nach Semantik, welche die Effizienz der Algorithmen steigern, implementiert.

In dieser Arbeit zeigen wir eine empirische Auswertung unserer Implementation der Algorithmen. Die Auswertung zeigt, dass je nach Größe und Struktur des Argumentationssystems ein Algorithmus effizienter ist als der andere. Die Optimierungen haben sehr gute Verbesserungen vor allem bei der conflict-free Semantik gezeigt, hatten allerdings bei admissible und stable keinen signifikanten Unterschied. Die Breitensuche und die Tiefensuche haben beide Vor- und Nachteile. Die Breitensuche ist effizienter als die Tiefensuche bei kleinen Argumentationssystemen (bis zu einer Größe von $10$ Argumenten) und die Tiefensuche ist effizienter bei komplexeren Systemen.


% You will typically include *both a German and an English abstract*.
% The rest of the document will be either in German or in English.

\cleardoublepage

\chapter*{\germanenglish{Danksagung}{Acknowledgements}}

I would like to express my deepest gratitude to everyone who supported me throughout the process of writing this thesis.

First and foremost, I would like to thank my supervisor, Johannes P. Wallner, for his invaluable guidance and for all the time he dedicated to supporting me throughout the process of completing this thesis. Thank you for all our insightful discussions in your office and for making it so easy for me to reach out and ask for your valuable feedback. Furthermore, I would like to thank Maria Eichlseder for the mentorship of my bachelor thesis and for all the valuable feedback you provided.

Thanks to all my friends I met at university, especially Simon, Martin, Lukas, and Timo, who were always there for productive discussions (sometimes even until late at night for some last-minute pre-deadline code changes).

I extend my appreciation to my friends in Graz besides university. Especially to my best-friend/roommate/uncarriable-teammate Felix, who was always there to distract me from what was important. I would also like to thank my friends Susanne and Katja for the time we spent together in Graz, where I was able to disconnect from my computer and enjoy time besides university.

Also, thank you to all my friends at home, especially Michael, for all the mathematical support and the countless chess games played together; Eva, for all the moral and medical support; and Mirjam, for always being there when I'm in need.

Finally, I would like to express my deepest gratitude to my beloved family. To my grandmothers, Nonna Gemma - \emph{Grazie per avermi sempre sostenuto e per tutte le candeline che mi hai acceso per ogni esame}; Oma Gertrud - \emph{Danke, dass du immer da warst und für all die leckeren Mahlzeiten}.

I would also like to thank my sister Sabrina for always being by my side and being the kindest person I know. Thank you for all the time we spent together; Having a lifelong sister and friend by my side has made my life so much easier.

Last but not least, I would like to thank my parents, my father - \emph{Grazie per avermi sostenuto e per darmi sempre la certezza di poter contare sul tuo supporto}; and my mother - \emph{Danke, dass du immer an mich geglaubt hast und mich an jeden meiner Schritte ermutigt und unterstützt hast}.

Without these great people, I wouldn't be the person who I am today. Thank You.



% ...

\cleardoublepage

\addtocontents{toc}{\vspace{-1em}}
\tableofcontents
\addtocontents{toc}{\vspace{-1em}}

\listoffigures

\listoftables

%% HERE ACRONYMS
\include{helper/acronyms}



%--- MAIN CONTENT --------------------------------------------------------------

\include{docs/Introduction}

\include{docs/Background}

\include{docs/Algorithm}

\include{docs/Implementation}

\include{docs/Experiments}

\include{docs/RelatedWorks}

\include{docs/Conclusion}


%--- BIBLIOGRAPHY --------------------------------------------------------------


% Print bibliography and include it in the table of contents:
\printbibliography
% An example bibliography file.
%
% This will create a separate file named "thesis-example.bib" and will overwrite
% its content on each compile run.
% If you already have your own bibliography file(s) or prefer to maintain
% thesis.bib separately, update the line "\addbibresource{\jobname.bib}" in the
% preamble and delete the following lines!

\end{document}
